---
title: "get_predictors_megachild"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tools)
library(glue)
library(broom)
library(stringr)
library(tidyverse)
library(lme4)
library(modelr)
library(purrr)


theme_set(theme_classic())
```

### Get AoA estimates
The following is based on the appendix D from the Wordbank book (Frank et al. 2019).
taken from: https://github.com/langcog/wordbank-book/blob/master/104-appendix-aoa.Rmd 
I use there Bayesian GLM with hand-tuned prior parameters model to get fitted AoA estimates on the English Words & Sentences data from Wordbank. (I take their data and model as is.)
```{r aoa_estimates}
load("../../../data/aoa_predictors/eng_ws_raw_data.Rds")

ms <- eng_ws %>%
  group_by(definition, age, category) %>%
  summarise(prop = mean(value == "produces", na.rm = TRUE), 
            num_true = sum(value == "produces", na.rm = TRUE), 
            num_false = sum(value != "produces", na.rm = TRUE), 
            n = sum(c(num_true, num_false))) %>%
  filter(!is.na(category))

fit_bglm <- function(data) {
  model <- arm::bayesglm(cbind(num_true, num_false) ~ age, 
                         family = "binomial", 
                         prior.mean = .3,
                         prior.scale = c(.01),
                         prior.mean.for.intercept = 0,
                         prior.scale.for.intercept = 2.5,
                         prior.df = 1,
                         data = data)
  aoa <- -model$coefficients[["(Intercept)"]] / model$coefficients[["age"]]
  
  tibble(definition = data$definition[1],
         category = data$category[1],
         bglm_slope = model$coefficients[["age"]],
         bglm_aoa = aoa)
}

bglm_aoas <- ms %>%
  split(.$definition) %>%
  map(fit_bglm) %>%
  bind_rows

```

### Get predictors from Braginsky et al. (2019) 

```{r get_predictors}

## Data from Braginsky et al. (2019)
load("../../../data/aoa_predictors/model_data.RData")
load("../../../data/aoa_predictors/uni_joined.RData")
uni_joined_eng <- uni_joined %>% filter(language == "English (American)")

```

### Get surprisal results from Megachild LSTM

```{r get_surprisal}

file = "../../../data/results/lstm-mega_child/Mega_child.aoa_result.csv"
df = read.csv(file)
#Extract child name from file name and add variable.
file_name = strsplit(file_path_sans_ext(file), "/")[[1]]
file_name = file_name[(length(file_name))]
child_name = strsplit(file_name,".aoa_result", fixed=TRUE)[[1]]
model_surprisals = df %>%
    mutate(child_name = child_name)

```

### Get frequency counts CHILDES child-directed speech data

```{r get_freq}
file = "../../../data/results/lstm-mega_child/Mega_child.aoa_freq.csv"
df = read.csv(file)
#Extract child name from file name and add variable.
file_name = strsplit(file_path_sans_ext(file), "/")[[1]]
file_name = file_name[(length(file_name))]
child_name = strsplit(file_name,".aoa_freq", fixed=TRUE)[[1]]
model_freq = df %>%
    mutate(child_name = child_name)

```

### Combine all predictors into one dataframe. Impute data (i.e. create estimates for missing values) and scale all predictors. 

```{r combine_pred}

surp_model_data <- model_surprisals %>% left_join(model_freq) %>% 
  mutate(avg_freq = frequency_count) %>% 
  select(uni_lemma, avg_surprisal, avg_freq, child_name) %>% 
  mutate(uni_lemma = as.character(uni_lemma)) %>% 
  left_join(ungroup(model_data)) %>% 
  group_by(child_name) %>%
  # mutate_at(vars(!!predictors), funs(as.numeric(scale(.)))) %>%
  nest()

predictors <- c("avg_surprisal", "avg_freq", "frequency", "MLU", "final_frequency", "solo_frequency", "num_phons", "concreteness", "valence", "arousal", "babiness")

pred_sources <- list(
  c("avg_surprisal", "avg_freq"),
  c("frequency", "MLU", "final_frequency", "solo_frequency"),
  c("valence", "arousal"),
  "concreteness", "babiness", "num_phons"
)

fit_predictor <- function(pred, d) {
  xs <- pred_sources %>% discard(~pred %in% .x) %>% unlist()
  x_str <- xs %>% paste(collapse = " + ")
  lm(as.formula(glue("{pred} ~ {x_str}")), data = d) %>%
    augment(newdata = d) %>%
    select(uni_lemma, lexical_category, .fitted)
}

max_steps <- 20
iterate_predictors <- function(lang_data) {
  missing <- lang_data %>%
    gather(predictor, value, !!predictors) %>%
    mutate(missing = is.na(value)) %>%
    select(-value) %>%
    spread(predictor, missing)
  predictor_order <- lang_data %>%
    gather(predictor, value, !!predictors) %>%
    group_by(predictor) %>%
    summarise(num_na = sum(is.na(value))) %>%
    filter(num_na != 0) %>%
    arrange(num_na) %>%
    pull(predictor)
  imputation_data <- lang_data %>%
    mutate_at(vars(!!predictors),
              funs(as.numeric(Hmisc::impute(., fun = "random"))))
  for (i in 0:max_steps) {
    pred <- predictor_order[(i %% length(predictor_order)) + 1]
    imputation_fits <- fit_predictor(pred, imputation_data)
    imputation_data <- missing %>%
      select(uni_lemma, lexical_category, !!pred) %>%
      rename(missing = !!pred) %>%
      right_join(imputation_data) %>%
      left_join(imputation_fits) %>%
      mutate_at(vars(pred), funs(if_else(is.na(missing), .fitted, .))) %>%
      select(-.fitted, -missing)
  }
  return(imputation_data)
}

model_data_imputed <- surp_model_data %>%
  mutate(imputed = map(data, iterate_predictors)) 

all_predictors_data <- model_data_imputed %>%
  select(-data) %>%
  unnest() %>%
  group_by(child_name) %>%
  mutate_at(vars(predictors), funs(as.numeric(scale(.))))


#save(model_data_imputed, file = "../../../data/aoa_predictors/model_data_imputed_mega_child.RData")
#save(all_predictors_data, file = "../../../data/aoa_predictors/all_predictors_data_mega_child.RData")

```

Join AoA estimates (dependent variable) to predictors together

```{r join_data}

aoa_estimates <- bglm_aoas %>% 
  mutate(words = tolower(definition),
         aoa = bglm_aoa) %>% 
  select(words, aoa)

#aoa_estimates <- empirical_aoas %>% 
#  mutate(words = tolower(definition),
#         aoa = empirical_aoa) %>% 
#  select(words, aoa)

data <- all_predictors_data %>% 
  left_join(aoa_estimates) %>% 
  filter(!is.na(aoa)) %>% 
  filter(lexical_category != "other") %>% ungroup()
  
#save(data, file = "../../../data/aoa_predictors/data_mega_child.RData")

```